

\section{Introduction}
The \textit{backbone} of a satisfiable formula is a set of literals that are true in all formula's models,
which plays an important role for understanding the hardness of problems in computation complexity.
For satisfiability problem~\cite{MZKST99},  backbone provides a good explanation for the apparent inevitably high cost of heuristic search near the phase boundary.
%For instance, the presence of backbones provides a good explanation for the apparent inevitably high cost of heuristic search near the phase boundary  for satisfiability problem \cite{MZKST99}.

The identification of backbone  has many practical applications. Backbone improves the performance of the random SAT solver like  WalkSAT~\cite{SBK1993} by making biased moves in a local search~\cite{ZWR2003,MAR2007}. In addition, backbone can significantly contributes to the Lin-Kernighan local search algorithms for Travel Salesman Problem~\cite{ZWL2005}. Another recent successful application of backbones is post-silicon fault localisation in integrated circuits~\cite{ZWSM11,ZWM11}.

However, deciding whether a literal is a backbone literal is co-NP complete~\cite{Jan10}. Many heuristic approaches were proposed to compute backbone in different setting, such as model enumeration, iterative SAT-testing and filtering with modern SAT solvers.
Marques-Silva et al. conducted an experimental evaluation by integration existing algorithms with optimisations in a modern SAT solver and showed that backbone computation for large practical formulae is feasible \cite{MJML2010,JLMS12,JLM15}.


In this paper, we propose a novel Greedy-Whitening based approach \tool for computing backbones. The insight of this approach has two-folds: 1) we present a fast procedure to compute an under-approximation set of non-backbone, which prunes the search space during the computation of backbone; 2) we also computes an approximation of backbone in polynomial time, and the elements in this set have high possibility to be  backbone literals which help us to  compute the exact backbone using SAT solvers.

We implemented our approach in a tool \tool and evaluated this tool with empirical experiments. We tested 72 satisfiable industrial formulae with time limits, the formulae are selected from SAT competitions during 2002 to 2016~\footnote{http://www.satcompetition.org/}.  \tool solved 34 from satisfiable industrial formulae in 3600 seconds and reduces 21\% total solving time comparing to \minibones. Especially, for benchmark \textit{mrpp}, \tool reduces 38\% solving time. On the other hand, we tested  6600 formulae generated automatically from 86 unsatisfiable formulae. We show that \tool is able to find more backbone quicker when the number of variables in the same clause of the formulae is in some range.
