\documentclass{IOS-Book-Article}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{amssymb,amsmath,amsthm,amsfonts}
\usepackage[vlined,ruled,linesnumbered,algo2e]{algorithm2e}

\usepackage{algpseudocode}
\usepackage{float}
\usepackage{tikz}
\usepackage{color}
\usepackage{calc}
\usepackage{subfig}

\usepackage{booktabs}
\usepackage{multirow}
\def\hb{\hbox to 10.7 cm{}}

\input{macro}
\begin{document}

\pagestyle{headings}
\def\thepage{}

\begin{frontmatter}              % The preamble begins here.


%\pretitle{Pretitle}
\title{Towards Backbone Computing: A Greedy-Whitening Based Approach}

\markboth{}{January 2017\hb}
%\subtitle{Subtitle}

\author[A]{\fnms{Yueling} \snm{Zhang}
% \thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
% 1013 BG Amsterdam, The Netherlands; E-mail:
% bookproduction@iospress.nl.}
},
\author[A]{\fnms{Min} \snm{Zhang}}
,
\author[A]{\fnms{Geguang} \snm{Pu}}
,
\author[B]{\fnms{Fu} \snm{Song}}
,
\author[A]{\fnms{Jianwen} \snm{Li}}

\address[A]{National Research Center of Trustworthy Embedded Software
        \\ East China Normal University, China}
\address[B]{School of Information Science and Technology ShanghaiTech University, China}

\begin{abstract}
%Propositional satisfiability (SAT) is widely used in both theoretical and practical applications in computer science. 
Backbone is the set of literals that are true in all formula's models.  Computing  backbone efficiently is the key to  accelerate SAT solving, which widely used in fault localization, product configuration and formula simplification.
In this paper, we propose a greedy-whitening based approach for computing backbone of propositional Boolean formulae.
The Greedy-based algorithm is constructed to compute an under-approximation of non-backbone. Moreover, we also propose 
a Whitening-based algorithm with two heuristic strategies to compute an approximation set of backbone.
The exact backbone is computed by applying iterative test backbone on the approximations.
We implemented our approach in a tool \tool and conducted experiments on instances from Industrial tracks of SAT Competitions
between 2002 and 2016. For industrial benchmarks, experimental results demonstrate that \tool solves as many 34 formulae as \minibones does (72 formulae in total in 3600 seconds), solves (49 formulae)  2 more formula than \minibones(47 formulae)(72 formulae in total in 16000 seconds).   In the case of 3600 seconds, \tool saved 18\% solving time in total.
\minibones performs better on \textit{mrpp} benchmark (4\% times faster), while \tool performs better on \textit{manthey} benchmark, saving 34\% solving time.
On the other side, we implemented our approach in a tool \tool and conducted experiments on instances from Uniform Random-3-SAT. Experiments with 6606 small formulae generated from 86 unsatisfiable formulae indicate that \tool is able to find more backbone quicker  when the number of variables in the same clause of the formulae is in some range.
\end{abstract}

\begin{keyword}
backbone\sep satisfiability\sep
approximation\sep greedy\sep whitening
\end{keyword}
\end{frontmatter}
\markboth{January 2017\hb}{January 2017\hb}


\input {intr.tex}
\input {prel.tex}
\input {overview.tex}
\input {greedy.tex}
\input {whitening.tex}
\input {expr.tex}
\input {relw.tex}
\input {conc.tex}

%\input {algorithm_unique_satisfy.tex}


\newpage

\bibliography{bib}

\begin{thebibliography}{99}

\bibitem{r1}
\textit{Scientific Style and Format: The CBE manual for authors,
editors and publishers}. Style Manual Committee, Council of Biology Editors.
Sixth ed. Cambridge University Press, 1994.

\bibitem{r2}
L.U. Ante, Cem surgere: Surgite postquam sederitis, qui manducatis panem doloris,
\textit{Omnes} \textbf{13} (1916), 114--119.

\bibitem{r3}
T.X. Confortavit, \textit{Seras}, Portarum, New York, 1995.

\bibitem{r4}
P.A. Deus, Ater hoc et filius et mater praestet nobis,
\textit{Paterhoc} \textbf{66} (1993), 856--890.

\end{thebibliography}
\end{document}
