\section{Preliminaries}\label{sec:prel}

We fix a finite set  $\X$ of \emph{Boolean variables}.
A \emph{literal} $l$ is either a Boolean variable $x\in \X$ or its negation $\neg x$.
The negation of a literal $\neg x$ is $x$, i.e., $\neg\neg x=x$.
A \emph{clause} $\phi$ is a disjunction of literals $\bigvee_{i=1}^n l_i$, which may be regarded as
the set of literals $\{l_i\mid 1\leq i\leq n\}$. W.l.o.g., we assume that for every
clause $\phi$, if $l\in\phi$, then $\neg l\not\in \phi$.

A \emph{formula} $\Phi$ over $\X$ is a Boolean combination of variables $\X$.
We assume that formulae are given in conjunctive normal
form (CNF), namely each formula $\Phi$ is a conjunction of clauses $\bigwedge_{i=1}^n\phi_i$ which may be regarded as a set of clauses $\{\phi_i\mid 1\leq i\leq n\}$. Given a formula $\Phi$, let $\var(\Phi)$ (resp. $\Lit(\Phi)$  and $\cls(\Phi)$) denote the set of variables (resp. literals and clauses) used in $\Phi$.
We use $\|\Phi\|$ to denote $\sum_{\phi\in\Phi}|\phi|$.
We use $\neg\Lit(\Phi)$ to denote the set $\{\neg l \mid l\in \Lit(\Phi)\}$.
The \emph{size} $|\Phi|$ of $\Phi$ is the number of literals of $\Phi$.
Given a formula $\Phi$ and a literal $l\in\Lit(\Phi)$,
let $\Phi_{l}\subseteq \Phi$ be the set of clauses $\{\phi\in\Phi\mid l\in\phi\}$.
Given two different variables $v_1, v_2\in\var(\Phi)$, $v_1$ and $v_2$ are adjacent variables iff there exists a clause $\phi\in\Phi$ such that $(v_1\in\phi)\wedge(v_2\in\phi)$.


An \emph{assignment} is a function $\lambda: \X \rightarrow \{0,1\}$, where $1$ (resp. $0$) denotes true (resp. false).
Given an assignment $\lambda$ and a literal $l$ that is $x$ or $\neg x$, let $\lambda[\neg l]$ be the assignment which is equal to $\lambda$
except for $\lambda[\neg l](x)=\neg \lambda(x)$. Given a set of variables $x=\{x_1,...,x_n\}$, let $\lambda[\neg L]$ denote the assignment
$\lambda[\neg x_1]...[\neg x_n]$.
An assignment $\lambda$ \emph{satisfies} a formula $\Phi$, denoted by $\lambda\models \Phi$, iff assigning $\lambda(x)$ to $x$ for $x\in\var(\Phi)$ makes $\Phi$ true.

\iffalse
An assignment $\lambda$ is a \emph{model} of $\Phi$ if $\lambda\models \Phi$.
Given two models $\lambda_1$ and $\lambda_2$ of $\Phi$, $\lambda_2$ can be \emph{generated} from $\lambda_1$, denoted by $\lambda_1\Rightarrow_\Phi\lambda_2$, if there exists a literal $l$ such that $\lambda_2=\lambda_1[\neg l]$.
Let $\Rightarrow^*_\Phi$ denote the \emph{reflexive transitive} closure of $\Rightarrow_\Phi$.
Formally, for every model $\lambda$ of $\Phi$, $\lambda\Rightarrow^*_\Phi\lambda$ and $\lambda_1\Rightarrow^*_\Phi\lambda_3$ if $\lambda_1\Rightarrow^*_\Phi\lambda_2$ and $\lambda_2\Rightarrow^*_\Phi\lambda_3$.
A \emph{model cluster} $\cl_\Phi(\lambda)$ of $\lambda$ is the set of models $\{\lambda'\mid \lambda\Rightarrow^*_\Phi\lambda'\}$.
A literal $l$ is a \emph{frozen literal} in a model $\lambda$ of $\Phi$,
if $l$ takes the same value in all the models of $\cl_\Phi(\lambda)$. Let $\FL(\Phi,\lambda)$ denote the set of all the frozen literals
in the model $\lambda$ of $\Phi$. %, and $\FL(\Phi)$ denote the intersection of $\FL(\Phi,\lambda)$ for all the models $\lambda$ of $\Phi$.
\fi

A formula $\Phi$ is \emph{satisfiable} iff there exists an assignment $\lambda$ such that $\lambda\models \Phi$.
Given a formula $\Phi$, the \emph{satisfiability problem} is to decide whether $\Phi$ is satisfiable or not.

\smallskip

\begin{definition}[Backbone]
\label{def:backbone}
Given a satisfiable formula $\Phi$, a literal $l$ is a \emph{backbone literal} of $\Phi$ iff for all assignments $\lambda$ such that $\lambda\models\Phi$,
$\lambda\models l$. The \emph{backbone} $\BL(\Phi)$ of $\Phi$ is the set of backbone literals of $\Phi$.
\end{definition}

\iffalse
Since a backbone literal takes same value in all the models and a frozen literal takes same value in a model cluster instead of all the models,
we get that:

\begin{proposition}\label{prop:Frozen-backbone}
For any formula $\Phi$ and model $\lambda$ of $\Phi$, $\BL(\Phi)\subseteq\FL(\Phi,\lambda)$.
\end{proposition}
Computing $\FL(\Phi,\lambda)$ of a given model is in polynomial time. However, the generation of the first model in each $\cl_\Phi(\lambda)$ still needs a SAT testing.
\fi

It is known that the backbone $\BL(\Phi)$ for each formula $\Phi$ is unique \cite{JLM15}.
The backbone of an unsatisfiable formula can be defined as an empty set. Therefore, in this work, we focus on satisfiable formulae.
We will use $\NBL(\Phi)$ to denote the set
$\Lit(\Phi)\setminus \BL(\Phi)$.

\begin{theorem}
\label{thm:co-NP}\cite{Jan10}
Given a satisfiable formula $\Phi$ and a literal $l$, deciding whether $l$ is a backbone literal is co-NP-complete.
\end{theorem}

\begin{definition}[Satisfied literal]
Given a model $\lambda$ of the formula $\Phi$ and a clause $\phi\in\Phi$, for each literal $l\in\phi$, $l$ is a \emph{satisfied literal}
of $\phi$ iff $\lambda\models l$. $l$ is a \emph{unique satisfied literal} of $\phi$ if there is no satisfied literal $l'$ of $\phi\setminus\{l\}$.
\end{definition}

Let us consider the formula $\Phi=\{\neg x_1 \vee \neg x_2, x_1, x_3 \vee x_4\}$,
$\var(\Phi)=\{x_1, x_2, x_3, x_4\}$, $\Lit(\Phi)=\{\neg x_1, x_1, \neg x_2, x_3, x_4\}$, $\Phi_{\neg x_2}=\{\neg x_1 \vee \neg x_2\}$ and $\BL(\Phi)=\{x_1, \neg x_2\}$.
Given a model $\lambda$ such that $\lambda(\neg x_1)=1,\lambda(\neg x_2)=0$. The satisfied literal of clause ($\neg x_1\vee\neg x_2$) is $\neg x_1$.

Given a formula $\Phi$ and a literal $l$, let $\Cnt(\Phi,l)$ denote the number of occurrence of $l$ in $\Phi$.
The \emph{density} $\dens(\Phi,l)$ of $l$ in $\Phi$ is defined as
\[
\dens(\Phi, l)=\frac{\Cnt(\Phi,l)}{\|\Phi_l\|}.
\]
